Phenotype pleiotropy of regulatory variants increases with the variety of bound transcription factors, regulated genes and active tissues

### 2022-08-21 ms/ms01_main.tex
ONGOING

For a posterior probability $\ge$ 0.8 that the GWAS variants and the eQTLs are common, we found TODO variants.
%
Our analysis suggests that these pleiotropic variants are under the control of more transcription factors and regulate more egenes in more etissues.

>>>>

For a posterior probability PP.H4.abf$\ge$0.8 of common causal eQTL and GWAS variants, we found 100,526 loci.
%
If I focus in causal variants with PP.H4.abf$\ge$0.8 and SNP.PP.H4$\ge$0.5, then I find 4684 variants.
%
Our analysis suggests that these pleiotropic variants are under the control of more transcription factors and regulate more egenes in more etissues.
